\documentclass[a4paper, serif, 11pt]{moderncv}

%% moderncv
% style and color
\moderncvstyle{banking}
\moderncvcolor{black}

% needed by moderncv for showing icons
\usepackage{fontawesome5}

%% page layout/margins
\usepackage[top=2.5cm, bottom=2.5cm, left=1.5cm, right=1.5cm]{geometry}
\nopagenumbers{}

%% fontspec
\usepackage{fontspec}

\IfFontExistsTF{Linux Libertine}{
  \setmainfont[Ligatures={TeX, Common}, Numbers=OldStyle]{Linux Libertine}
}{}
\IfFontExistsTF{Linux Libertine O}{
  \setmainfont[Ligatures={TeX, Common}, Numbers=OldStyle]{Linux Libertine O}
}{}

%% CTeX
% CJK support, used to show CJK characters in the resume
%
% - fontset=none: disable builtin fontset but instead set the CJK font manually
% - heading=false: disable ctex heading
% - punct=kaiming: use kaiming punctuations styles for CJK
% - scheme=plain: use plain scheme, do not override `\normalsize` font size
% - space=auto: space settings for CJK characters
%
% ref:
% - http://ctan.mirrorcatalogs.com/language/chinese/ctex/ctex.pdf
\usepackage[UTF8, fontset=none, heading=false, punct=kaiming, scheme=plain, space=auto]{ctex}

\IfFontExistsTF{Noto Serif CJK SC}{
  \setCJKmainfont{Noto Serif CJK SC}
}{}
\IfFontExistsTF{Noto Sans CJK SC}{
  \setCJKsansfont{Noto Sans CJK SC}
}{}

\usepackage{tcolorbox}

% Define a custom section command
\newcommand{\boxedsection}[1]{%
  \begin{tcolorbox}[
    colback=red!10,
    colframe=red!50,
    arc=0pt,
    outer arc=0pt,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    boxrule=2pt
  ]
    \section{#1}
  \end{tcolorbox}
}

\name{Jane Doe}{}
\title{Senior Software Engineer}
\phone[mobile]{555-123-4567}
\email{jane.doe@example.com}

\begin{document}

\maketitle

\boxedsection{Basics}

\cvline{}{A passionate and experienced software engineer with a proven track record of designing, developing, and deploying robust web applications. Skilled in both front-end and back-end development, with a keen eye for detail and a dedication to writing clean, efficient code.}

\boxedsection{Professional Experience}

\cventry{Jul 2020 -- Present}
        {Senior Software Engineer}
        {Tech Solutions Inc.}
        {}
        {}
        {\begin{itemize}
\item Led the development of a new microservices-based architecture, improving system scalability and reliability.
\item Mentored junior engineers, providing guidance on best practices and code quality.
\item Optimized application performance, reducing API response times by 30\%. 
\end{itemize}}

\cventry{Jul 2018 -- Jun 2020}
        {Software Engineer}
        {Innovate Corp.}
        {}
        {}
        {\begin{itemize}
\item Developed and maintained features for a large-scale e-commerce platform using React and Node.js.
\item Collaborated with product managers and designers to deliver high-quality user experiences.
\item Participated in on-call rotation to ensure application stability.
\end{itemize}}

\cventry{Jun 2017 -- Aug 2017}
        {Software Engineer Intern}
        {Data Systems LLC}
        {}
        {}
        {\begin{itemize}
\item Assisted in the development of a data processing pipeline.
\item Wrote unit tests to ensure code quality.
\item Gained experience with Agile development methodologies.
\end{itemize}}

\boxedsection{Academic Background}

\cventry{Sep 2018 -- Jun 2020}
        {Master, Software Engineering}
        {Tech University}
        {}
        {}
        {Specialized in distributed systems and cloud computing.}

\cventry{Sep 2014 -- Jun 2018}
        {Bachelor, Computer Science}
        {State University}
        {}
        {}
        {\begin{itemize}
\item Graduated with honors.
\item Focused on algorithms, data structures, and distributed systems.
\end{itemize}
\textbf{Courses}: Data Structures \& Algorithms, 
Operating Systems, 
Computer Networks, 
Database Systems}

\boxedsection{Technical Skills}

\cvline{Programming Languages}{Expert \hfill \textbf{Keywords}: JavaScript (ES6+), TypeScript, Python, Go}
\cvline{Technologies \& Frameworks}{Advanced \hfill \textbf{Keywords}: React, Node.js, Express, Docker, Kubernetes, PostgreSQL}
\cvline{Developer Tools}{Advanced \hfill \textbf{Keywords}: Git \& GitHub, Webpack, Jest, CircleCI}

\section{Languages}

\cvline{English}{Native or Bilingual Proficiency}
\cvline{Spanish}{Limited Working Proficiency}
\end{document}
